A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-23 paper.Rmd
done with 4.2.3

Participants for all three data collection periods are recruited from an crowdsourcing platform called Prolific [@palan2018prolific]. Prescreening procedure is applied during the recruitment, participants are required to be fluent in English, with $98\%$ minimum approval rate and 10 minimum submissions in other studies.

During the experiment, every participant is presented with a block of 20 lineups. A lineup consists of a randomly placed data plot and 19 null plots, which are all residual plots drawn with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line is added at $y = 0$ as a helping line.

The data of the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{visual-test-procedure-based-on-lineups}.

In every lineup evaluation, the participant is asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, participants are permitted to select zero plots without providing the reason. No participant are shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiments are also collected. A participant's submission is only accepted if the data plot is identified for at least one attention check. Data of rejected submissions are discarded automatically to maintain the overall data quality.

>>>>

Participants for all three data collection periods were recruited from the Prolific crowd-sourcing platform [@palan2018prolific]. Pre-screening procedures were applied during the recruitment: participants were required to be fluent in English, with $98\%$ minimum approval rate and at least 10 submissions in other studies.

During the experiment, every participant is presented with a block of 20 lineups. A lineup consists of a randomly placed data plot and 19 null plots, which are all residual plots drawn with raw residuals on the y-axis and fitted values on the x-axis. An additional horizontal red line is added at $y = 0$ as a visual reference. The data in the data plot is simulated from one of two models described in Section \ref{simulating-departures-from-good-residuals}, while the data of the remaining 19 null plots are generated by the residual rotation technique discussed in Section \ref{visual-test-procedure-based-on-lineups}.

In each lineup evaluation, the participant was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, participants were permitted to select zero plots without providing the reason. No participant was shown the same lineup twice. Information about preferred pronouns, age group, education, and previous experience in visual experiments were also collected. A participant's submission was only included in the analysis if the data plot is identified for at least one attention check. <!--Data of rejected submissions are discarded automatically to maintain the overall data quality.-->

### 2023-04-23 paper.tex
done with 4.2.3

Participants for all three data collection periods are recruited from an
crowdsourcing platform called Prolific \citep{palan2018prolific}.
Prescreening procedure is applied during the recruitment, participants
are required to be fluent in English, with \(98\%\) minimum approval
rate and 10 minimum submissions in other studies.

During the experiment, every participant is presented with a block of 20
lineups. A lineup consists of a randomly placed data plot and 19 null
plots, which are all residual plots drawn with raw residuals on the
y-axis and fitted values on the x-axis. An additional horizontal red
line is added at \(y = 0\) as a helping line.

The data of the data plot is simulated from one of two models described
in Section \ref{simulating-departures-from-good-residuals}, while the
data of the remaining 19 null plots are generated by the residual
rotation technique discussed in Section
\ref{visual-test-procedure-based-on-lineups}.

In every lineup evaluation, the participant is asked to select one or
more plots that are most different from others, provide a reason for
their selections, and evaluate how different they think the selected
plots are from others. If there is no noticeable difference between
plots in a lineup, participants are permitted to select zero plots
without providing the reason. No participant are shown the same lineup
twice. Information about preferred pronoun, age group, education, and
previous experience in visual experiments are also collected. A
participant's submission is only accepted if the data plot is identified
for at least one attention check. Data of rejected submissions are
discarded automatically to maintain the overall data quality.

>>>>

Participants for all three data collection periods were recruited from
the Prolific crowd-sourcing platform \citep{palan2018prolific}.
Pre-screening procedures were applied during the recruitment:
participants were required to be fluent in English, with \(98\%\)
minimum approval rate and at least 10 submissions in other studies.

During the experiment, every participant is presented with a block of 20
lineups. A lineup consists of a randomly placed data plot and 19 null
plots, which are all residual plots drawn with raw residuals on the
y-axis and fitted values on the x-axis. An additional horizontal red
line is added at \(y = 0\) as a visual reference. The data in the data
plot is simulated from one of two models described in Section
\ref{simulating-departures-from-good-residuals}, while the data of the
remaining 19 null plots are generated by the residual rotation technique
discussed in Section \ref{visual-test-procedure-based-on-lineups}.

In each lineup evaluation, the participant was asked to select one or
more plots that are most different from others, provide a reason for
their selections, and evaluate how different they think the selected
plots are from others. If there is no noticeable difference between
plots in a lineup, participants were permitted to select zero plots
without providing the reason. No participant was shown the same lineup
twice. Information about preferred pronouns, age group, education, and
previous experience in visual experiments were also collected. A
participant's submission was only included in the analysis if the data
plot is identified for at least one attention check.
